---
title: "About"
output: html_document
bibliography: bib.bib
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
nocite: |
   @Hwang:2019bn, @MAGICconsortium:2011dl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(PubMedWordcloud)
author <- "Kyu-Baek Hwang"
pmid <- getPMIDs(author = author, dFrom = 2002, dTo = 2018, n = 200)
abstracts <- getAbstracts(pmid)
words <- cleanAbstracts(abstracts)

words <- dplyr::filter(words, word != 'developed' & word != 'high' & word != 'patient' & word != 'associated' & word != 'identified' & word != 'found' & word != 'performed' & word != 'potential' & word != 'including' & word != 'results' & word != 'developed' & word != 'available' & word != 'compared' & word != 'can' & word != 'may' & word != 'study' & word != 'associated' & word != 'one' & word != 'two' & word != 'first' & word != 'however' & word != 'used' & word != 'analyzed' & word != 'patients' & word != 'years' & word != 'present' & word != 'subsequent' & word != 'age' & word != 'whether' & word != 'use')
words400 <- words[1:400, ]

```

<p>I am a software engineer working in [NGeneBio](http://www.ngenebio.com) in Seoul, Korea. Most of my activities involve cancer data science, i.e. analysis of data from high-throughput molecular profiling of tumor samples. </p>

<p>Main ongoing research activities:

   * Cancer genome interpretation

   * NGS Analysis pipeline

   * Clinical software developement

   * Cloud computing

<br>
<p>
A wordcloud of papers I have co-authored:
<br/>
[@Hwang:2019bn]
[@MAGICconsortium:2011dl]

</p>
```{r publication_word_cloud, echo = F, message=FALSE, warning=FALSE}
plotWordCloud(words400[], rot.per = 0, scale = c(5,0.3))
```